Portal Forecast

### 2018-04-13 index.Rmd

data = compile_forecasts()
ensemble = dplyr::filter(data, level == 'Controls', model == 'Ensemble', date == max(date))
sp_predictions = get_sp_predicts(ensemble, 'Controls', lead_time = 1)
sp_predict = plot_species_forecast(sp_predictions,
            title=paste0(sp_predictions$forecast_date[2], ": Control plots"))

>>>>

data = compile_forecasts()
ensemble = dplyr::filter(data, level == 'Controls', model == 'Ensemble', date == max(date))
sp_predictions = get_sp_predicts(ensemble, 'Controls', 
            lead_time = length(unique(ensemble$newmoonnumber)) - 11)
sp_predict = plot_species_forecast(sp_predictions,
            title=paste0(sp_predictions$forecast_date[2], ": Control plots"))
